---
title: "Medical Charge Predictions"
output: html_document
date: "2024-10-25"
By: Osama Jabr
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Loading the data

```{r}
df = read.csv('insurance.csv', header=TRUE)
num_cols <- unlist(lapply(df, is.numeric))
plot((df[,num_cols]))
```

### Calculating the correlation coefficients between all numeric columns in the dataset:
```{r}
round(cor(df[,num_cols]),2)
```
### Model evaluation

Generating a summary of the linear model to review detailed statistical information about the model's coefficients and performance metrics, aiding in assessing the impact of various predictors on medical charges.
```{r}
smoker = as.factor(df$smoker)
sex = as.factor(df$sex)
region = as.factor(df$region)

boxplot(df$charges ~ smoker, main = "Smoker")
boxplot(df$charges ~ sex, main = "sex")
boxplot(df$charges ~ region, main = "region")

```

### Fitting the model:
Fitting a comprehensive linear model to the data to predict `charges` based on all available explanatory variables in the dataset, to understanding which variables are significant predictors and how they relate to the cost of healthcare.

```{r}

model1 = lm(charges ~ ., data = df)

```

### Summary of the model:
```{r}
summary(model1)
```

